Usage metrics

### 2020-12-17 analysis/usage.Rmd
Density of amount of computations. Ranking per type

```{r select-columns, message=TRUE, warning=FALSE, include=FALSE}
E_raw %>% select(
  run_package = package, #      The package which was run to trigger the eval
  ev_variant = eval_function, # Which eval variant was called
  duplicates = nb_ev_calls, #   Number of identical eval calls (weight)
  src_ref = eval_call_srcref, # Source ref for the eval call site
  file, #                       Script file name (name of this run)
  ev_package = eval_source, #   Package of the call site
  arg_size = expr_resolved_length, #   Size in bytes of eval argument string
  opcodes = direct_interpreter_eval #  Count of the AST nodes traversed by the
) -> E #                               interpreter during eval (non-recursive).

@@

tmp <- sites_per_variant %>% filter(ev_variant == "eval")
dyn_evl <- if (nrow(tmp)==0) { 0 } else { tmp$n }
tmp <- sites_per_variant %>% filter(ev_variant == "evalq")
dyn_evq <- if (nrow(tmp) == 0) { 0 } else { tmp$n }
tmp <- sites_per_variant %>% filter(ev_variant == "eval.parent") 
dyn_evp <- if(nrow(tmp) == 0) { 0 } else { tmp$n }
tmp <- sites_per_variant %>% filter(ev_variant == "local")
dyn_loc <- if(nrow(tmp) == 0) { 0 } else { tmp$n }

@@

```{r ev-dist, include=FALSE}
# The calls per package
pack_calls <- E %>% count(ev_package, wt=duplicates, sort = TRUE)
# Create bins at every power of ten
bins <- cut(pack_calls$n, breaks = c(0, 10^seq(1,8)), include.lowest = TRUE)
sum <- summary(bins)
# Packages with more than 1K calls
Kcalls <- pack_calls %>% filter(n > 1000) %>% nrow()

@@

# Number of eval calls per package
ecpp <- pack_calls %>% left_join(runs, by = "ev_package") 
stopifnot( nrow(filter(ecpp, n==0)) == 0)
# The package with the most calls
max_calls <- ecpp %>% filter(n == max(n))

@@

sizes_prop %>%
  ggplot(aes(x=arg_size)) + geom_histogram()

```

@@

```{r amount_computations, include=F}
tot_events <- E %>% summarise(n=sum(opcodes)) %>% .$n
max_events <- E %>% summarize(n = max(opcodes)) %>% .$n

@@

E %>%
  filter(opcodes > 50) %>%
  ggplot(aes(x = "", y = opcodes, fill = ""), na.rm = TRUE) +
  geom_violin(trim = FALSE, width = 1.7) +
  scale_y_log10(labels = scales::comma) +
  labs(y = "", x="") +
  theme(legend.position = "none")

@@

E %>%
  filter(opcodes > 0) %>%
  filter(opcodes < 50) %>%
  ggplot(aes(x = "", y = opcodes, fill = ""), na.rm = TRUE) +
  geom_violin(trim = FALSE, width = 1.7) +
  labs(y = "Events per package", x="") +
  theme(legend.position = "none")

@@

# For each site, how many runs and within each runs how often do we trigger.
triggered <- E %>%
  group_by(src_ref) %>%
  summarize(n_runs = n_distinct(file), 
            n = sum(duplicates), 
            average = n / n_runs) %>%
  arrange(desc(average))

@@

bins <- cut(triggered$average, breaks = c(0, 50, 100, 250,500, 1000, 1500,  2000, 3000), include.lowest = TRUE)
sum <- summary(bins)

@@

>>>>

```{r select-columns, message=TRUE, warning=FALSE, include=FALSE}
E_raw %>% select(
  run_package = package, #      The package which was run to trigger the eval
  ev_variant = eval_function, # Which eval variant was called
  duplicates = nb_ev_calls, #   Number of identical eval calls (weight)
  src_ref = eval_call_srcref, # Source ref for the eval call site
  file, #                       Script file name (name of this run)
  ev_package = eval_source, #   Package of the call site
  arg_size = expr_resolved_length, #   Size in characters (unicode) of eval argument string
  type = expr_resolved_type_tag,
  opcodes = direct_interpreter_eval #  Count of the AST nodes traversed by the
) -> E #                               interpreter during eval (non-recursive).

@@

tmp <- sites_per_variant %>% filter(ev_variant == "eval")
dyn_evl <- if (nrow(tmp) == 0) {
  0
} else {
  tmp$n
}
tmp <- sites_per_variant %>% filter(ev_variant == "evalq")
dyn_evq <- if (nrow(tmp) == 0) {
  0
} else {
  tmp$n
}
tmp <- sites_per_variant %>% filter(ev_variant == "eval.parent")
dyn_evp <- if (nrow(tmp) == 0) {
  0
} else {
  tmp$n
}
tmp <- sites_per_variant %>% filter(ev_variant == "local")
dyn_loc <- if (nrow(tmp) == 0) {
  0
} else {
  tmp$n
}

@@

```{r ev-dist, include=FALSE}
# The calls per package
pack_calls <- E %>% count(ev_package, wt = duplicates, sort = TRUE)
# Create bins at every power of ten
bins <- cut(pack_calls$n, breaks = c(0, 10^seq(1, 8)), include.lowest = TRUE)
sum <- summary(bins)
# Packages with more than 1K calls
Kcalls <- pack_calls %>%
  filter(n > 1000) %>%
  nrow()

@@

# Number of eval calls per package
ecpp <- pack_calls %>% left_join(runs, by = "ev_package")
stopifnot(nrow(filter(ecpp, n == 0)) == 0)
# The package with the most calls
max_calls <- ecpp %>% filter(n == max(n))

@@

sizes_prop %>%
  ggplot(aes(x = arg_size)) +
  geom_histogram()

E %>%
  ggplot(aes(x = arg_size)) +
  stat_density(aes(y = ..count..), color = "black", fill = "blue", alpha = 0.3) +
  scale_x_continuous(breaks = c(0, 1, 2, 3, 4, 5, 10, 30, 100, 300, 1000), trans = "log1p", expand = c(0, 0)) +
  labs(x = "Size (characters)")

ggsave(path(PLOT_DIR, "size_loaded_distribution.pdf"))
```

@@

```{r amount_computations, include=F}
tot_events <- E %>%
  summarise(n = sum(opcodes * duplicates)) %>%
  .$n
max_events <- E %>%
  summarize(n = max(opcodes)) %>%
  .$n

@@

E %>%
  filter(opcodes > 50) %>%
  ggplot(aes(x = "", y = opcodes, fill = ""), na.rm = TRUE) +
  geom_violin(trim = FALSE, width = 1.7) +
  scale_y_log10(labels = scales::comma) +
  labs(y = "", x = "") +
  theme(legend.position = "none")

@@

E %>%
  filter(opcodes > 0) %>%
  filter(opcodes < 50) %>%
  ggplot(aes(x = "", y = opcodes, fill = ""), na.rm = TRUE) +
  geom_violin(trim = FALSE, width = 1.7) +
  labs(y = "Events per package", x = "") +
  theme(legend.position = "none")

@@

# For each site, how many runs and within each runs how often do we trigger.
triggered <- E %>%
  group_by(src_ref) %>%
  summarize(
    n_runs = n_distinct(file),
    n = sum(duplicates),
    average = n / n_runs
  ) %>%
  arrange(desc(average))

@@

bins <- cut(triggered$average, breaks = c(0, 50, 100, 250, 500, 1000, 1500, 2000, 3000), include.lowest = TRUE)
sum <- summary(bins)

@@

How diverse are the expressions passed to `eval`? We consider the diversity in types in the resolved expression.

```{r type-diversity}
E %>%
  ggplot(aes(x = fct_rev(fct_infreq(type)))) +
  geom_bar() +
  coord_flip() +
  labs(x = "type")
```
